\bibitem{anova}
E.~R. Girden, \emph{ANOVA: Repeated measures}.\hskip 1em plus 0.5em minus
  0.4em\relax Sage, 1992, no.~84.

\bibitem{mutual-info}
A.~Kraskov, H.~St{\"o}gbauer, and P.~Grassberger, ``Estimating mutual
  information,'' \emph{Physical review E}, vol.~69, no.~6, p. 066138, 2004.

\bibitem{decisiontrees}
L.~Breiman, \emph{Classification and regression trees}.\hskip 1em plus 0.5em
  minus 0.4em\relax Routledge, 2017.

\bibitem{randomforests}
------, ``Random forests,'' \emph{Machine learning}, vol.~45, no.~1, pp. 5--32,
  2001.

\bibitem{mlp}
G.~E. Hinton, ``Connectionist learning procedures,'' in \emph{Machine Learning,
  Volume III}.\hskip 1em plus 0.5em minus 0.4em\relax Elsevier, 1990, pp.
  555--610.

\bibitem{adaboost}
Y.~Freund and R.~E. Schapire, ``A decision-theoretic generalization of on-line
  learning and an application to boosting,'' \emph{Journal of computer and
  system sciences}, vol.~55, no.~1, pp. 119--139, 1997.

\bibitem{franzin2017effect}
A.~Franzin, L.~P. C{\'a}ceres, and T.~St{\"u}tzle, ``Effect of transformations
  of numerical parameters in automatic algorithm configuration,''
  \emph{Optimization Letters}, pp. 1--13, 2017.

\bibitem{fashion}
H.~Xiao, K.~Rasul, and R.~Vollgraf. (2017) Fashion-mnist: a novel image dataset
  for benchmarking machine learning algorithms.

\bibitem{svhn}
Y.~Netzer, T.~Wang, A.~Coates, A.~Bissacco, B.~Wu, and A.~Y. Ng, ``Reading
  digits in natural images with unsupervised feature learning,'' 2011.

\bibitem{cifar}
A.~Krizhevsky, G.~Hinton \emph{et~al.}, ``Learning multiple layers of features
  from tiny images,'' Citeseer, Tech. Rep., 2009.

\bibitem{lmrd}
\BIBentryALTinterwordspacing
A.~L. Maas, R.~E. Daly, P.~T. Pham, D.~Huang, A.~Y. Ng, and C.~Potts,
  ``Learning word vectors for sentiment analysis,'' in \emph{Proceedings of the
  49th Annual Meeting of the Association for Computational Linguistics: Human
  Language Technologies}.\hskip 1em plus 0.5em minus 0.4em\relax Portland,
  Oregon, USA: Association for Computational Linguistics, June 2011, pp.
  142--150. [Online]. Available: \url{http://www.aclweb.org/anthology/P11-1015}
\BIBentrySTDinterwordspacing

\bibitem{reuters}
D.~Lewis, ``Reuters-21578 text categorization test collection, distribution
  1.0,''
  \emph{http://www.daviddlewis.com/resources/testcollections/reuters21578/},
  1997.

\bibitem{agnews}
X.~Zhang, J.~Zhao, and Y.~LeCun, ``Character-level convolutional networks for
  text classification,'' \emph{arXiv preprint arXiv:1509.01626}, 2015.
